\EVOSUITE at the SBST 2017 Tool Competition

### 2017-02-22 papers/sbst17/paper_sbst17.tex
TODO
new data for manual tests

\ifdraft
	\marginparwidth=1.3cm
	\marginparsep=5pt
	\newcommand\remark[1]{%
		\mymarginpar{\raggedright\hbadness=10000\tiny\it #1\par}}
\else
	\newcommand\remark[1]	{}
\fi

@@

% TODO marker
\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}

@@

This year, the contest also included manually written test suites as
baseline. \EVOSUITE significantly outperformed this manual baseline as
well, both in terms of branch coverage (avg. \AvgCovEvosuite vs
\AvgCovManual, with Vargha-Delaney's $A_{12}=\EvoManCovA$ and
$p\EvoManCovPV$) and mutation scores (avg. \AvgMutEvosuite vs
\AvgMutManual, with $A_{12}=\EvoManMutA$ and
$p\EvoManMutPV$).\TODO{Does showing A12 make sense if there's only one
  manual test suite per benchmark?}

@@

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Techniques such as
\textit{partial minimisation} to only select a few test cases to be
minimised, rather than all test cases, or more efficient minimisation
based on \textit{delta-debugging}~\cite{LOZCM07}, might be worth
investigating to alleviate this issue.

>>>>

\ifdraft
	\marginparwidth=1.3cm
	\marginparsep=5pt
	\newcommand\remark[1]{%
		\mymarginpar{\raggedright\hbadness=10000\tiny\it #1\par}}
	% TODO marker
	\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}
\else
	\newcommand\remark[1]	{}
	\newcommand{\TODO}[1]{}
\fi

@@

@@

This year, the contest also included manually written test suites as
baseline (only for 63 out of the 69 benchmarks). The results indicate
that there is no significant difference in branch coverage between
\EVOSUITE-generated test suites (avg. \AvgCovEvosuite) and manually
written ones (avg. \AvgCovManual), with Vargha-Delaney's
$A_{12}=\EvoManCovA$ and $p=\EvoManCovPV$. In terms of mutation
scores, however, the results show
that---unsurprisingly---automatically generated assertions are weaker
than manually written ones: the average \EVOSUITE mutation score for
these 63 benchmarks is \AvgMutEvosuite, significantly lower than the
average \AvgMutManual obtained by developer-written test suites, with
$A_{12}=\EvoManMutA$ and $p\EvoManMutPV$.\TODO{Does showing A12 make
  sense if there's only one manual test suite per benchmark?}

@@

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to its previous, unminimised version, which as
mentioned before is more likely to break. A \textit{partial
  minimisation} approach to select and minimise only a reduced subset
of tests, or a more efficient minimisation approach based on
\textit{delta-debugging}~\cite{LOZCM07}, might be worth exploring to
alleviate this issue.
